Type Refinements for the Working Class

### 2015-11-09 paper.tex
formatting

The second judgment is defined coinductively via the following meaning
explanation:
\begin{quote}
  To know $\Refines{\Phi}{\phi}{\tau}$ (presupposing
  $\RefinesCtx{\Phi}{\Upsilon}$ and $\IsSort{\tau}$) is to know, for any renaming
  $\Of{\varrho}{\Upsilon\hookrightarrow\OMode{\Upsilon'}}$, for any $M, N$,
  what it means for $M$ and $N$ to be identified under $\phi$, supposing
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$, requiring that if
  $\IMode{M}\sim_\phi\IMode{N}$ then $\IMode{N}\sim_\phi\IMode{M}$, and if
  $\IMode{M}\sim_\phi\IMode{N}$ and $\IMode{N}\sim_\phi\IMode{O}$, then
  $\IMode{M}\sim_\phi\IMode{O}$.
\end{quote}

>>>>

The second judgment is defined coinductively via the following meaning
explanation:
\begin{definition}[Refinement]
  To know $\Refines{\Phi}{\phi}{\tau}$ (presupposing
  $\RefinesCtx{\Phi}{\Upsilon}$ and $\IsSort{\tau}$) is to know, for any renaming
  $\Of{\varrho}{\Upsilon\hookrightarrow\OMode{\Upsilon'}}$, for any $M, N$,
  what it means for $M$ and $N$ to be identified under $\phi$, supposing
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$, requiring that if
  $\IMode{M}\sim_\phi\IMode{N}$ then $\IMode{N}\sim_\phi\IMode{M}$, and if
  $\IMode{M}\sim_\phi\IMode{N}$ and $\IMode{N}\sim_\phi\IMode{O}$, then
  $\IMode{M}\sim_\phi\IMode{O}$.
\end{definition}
